Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-08 paper/abstraction/paper.tex
rewrite preference search section

Tagging and filtering according to the PG with community values in BGP allows the protocol to only search for paths to the destination that are allowed by the policy. However, finding \emph{some} path to the destination is not enough. We must ensure that each router uses the \emph{best} path to the destination according to the policy. Further, this must continue to hold as elements of the network fail. To this end, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.

The idea then is to have each router totally order advertisements from different neighbors (possibly with different tags). For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2. Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use. Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
\Propane introduced a conservative search strategy for determining route preferences. To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:

>>>>

Tagging and filtering according to the PG with community values in BGP forces the protocol to only search for paths to the destination that are allowed by the policy (\IE are paths in the PG). However, finding \emph{some} path to the destination is not enough. We must ensure that each router uses its \emph{best} available path to the destination according to the policy. Further, this must continue to hold as additional elements of the network fail. In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup. If router S1 allows advertisements from both N1 and N2 but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{ties between equally preferred paths can be broken nondeterministic based on message ordering}. On the other hand, if the S1-N1 link fails, then the best available path is through N2.

To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor. The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.

The idea then is to search for such a device-local preference function for each router that totally order advertisements from different neighbors (possibly with different tags). For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2. Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$. Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which is more preferred than automata 2. Further, it can result in downstream routers such as A1 receiving a message in a more preferred state $(A1,1,0)$ instead of $(A1,0,1)$.

In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem. \Propane introduced a conservative search strategy for determining route preferences that works well in practice. To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
